The Power of Two Random Choices\\ \large A follow up seminar to the Parallel Algorithms lecture\footnote{Jesper Larsson Träff, lecture ``Parallel Algorithms'', 2012 winter term at TU Wien.}

### 2014-01-26 article/article.tex
intro for greedy and always-go-left

Thus, let $B$ be the set of bins $\{1,2...n\}$, $\Omega = B^{d}$ be the sample space and $\mathcal{F} = 2^{\Omega}$ be the set of measurable events. We are only interested in events that represent a set of bins of size $d$. Thus, let $\mathcal{F}_d = \{\mathcal{E} \in \mathcal{F}: \left\vert \mathcal{E} \right\vert = d\}$ and set $\Pr\left(\mathcal{E}  \right) = 0$  $\forall \mathcal{E} \in \mathcal{F} \setminus \mathcal{F}_d $. The three classes of algorithms are distinguished by the probability function $\Pr\left(\mathcal{E}\right)$ for events $\mathcal{E}_d \in \mathcal{F}_d$:
\begin{itemize}
\item \emph{Uniform and independent.} Choose each of the $d$ bins for a ball uniformly and independently at random from the set of bins $B$. This implies 
\[
\forall \mathcal{E} \in \mathcal{F}_d: \Pr\left(\mathcal{E}\right) = \frac{1}{n ^{d}}
\]
\item \emph{Non-uniform and independent.} Choose the $i$th bin from $B$ independently at random according to some probability function
\[
\Pr: B \rightarrow \left[0,1\right]
\]

\item \emph{Non-uniform and dependent.} Choose the $d$ bins for a ball from $\Omega$ at random:
\[
\Pr: B^{d} \rightarrow \left[0,1\right]
\]

@@

We will discuss two different multiple-choice schemes: The \emph{Greedy$[d]$} scheme (Section \ref{sec:greedy}) places the ball into the least full bin among $d$ bins chosen uniformly and independently at random whereas the \emph{Always-Go-Left} scheme (Section \ref{sec:AlwaysGoLeft}) uses a nonuniform selection of $d$ bins.

>>>>

Thus, let $B$ be the set of bins $\{1,2...n\}$, $\Omega = B^{d}$ be the sample space and $\mathcal{F} = 2^{\Omega}$ be the set of measurable events. We are only interested in events that represent a set of bins of size $d$. Thus, let $\mathcal{F}_d = \{\mathcal{E} \in \mathcal{F}: \left\vert \mathcal{E} \right\vert = d\}$ and set $\Pr\left(\mathcal{E}  \right) = 0$  $\forall \mathcal{E} \in \mathcal{F} \setminus \mathcal{F}_d $. The three classes of algorithms are distinguished by the probability function $\Pr\left(\mathcal{E}\right)$ for events $\mathcal{E} \in \mathcal{F}_d$:
\begin{itemize}
\item  \emph{Uniform and independent.} Choose each of the $d$ bins for a ball uniformly and independently at random from the set of bins $B$. This implies 
\[
\forall \mathcal{E} \in \mathcal{F}_d: \Pr\left(\mathcal{E}\right) = \frac{1}{n ^{d}}
\]
\item Class 2: \emph{Non-uniform and independent.} Choose the $i$th bin from $B$ independently at random according to some probability function
\[
\Pr: B \rightarrow \left[0,1\right]
\]

\item Class 3: \emph{Non-uniform and dependent.} Choose the $d$ bins for a ball from $\Omega$ at random:
\[
\Pr: B^{d} \rightarrow \left[0,1\right]
\]

@@

We will discuss two different multiple-choice placement strategies: The \emph{Greedy} algorithm (Section \ref{sec:greedy}) belongs to class 1, whereas the \emph{Always-Go-Left} scheme (Section \ref{sec:AlwaysGoLeft}) uses a non-uniform and independent selection of $d$ bins and thus belongs to class 2.
